### 2014-01-13 manuscripts/dpp-msbayes/dpp-msbayes-tables.tex
Working on model tables for dpp manuscript.

\begin{table}[htbp]
    \sffamily
    % \footnotesize
    \addtolength{\tabcolsep}{-0.08cm}
    \rowcolors{2}{}{myGray}
    %\captionsetup{font=footnotesize}
    \caption{The model priors evaluated in our simulation-based analyses.  For
        the \modelDPP model, the prior on the concentration parameter,
        $\concentrationParam \sim Gamma(\cdot,\cdot)$, was set to $Gamma(2,2)$
        for the validation analyses and $Gamma(1.5,18.1)$ for the power
        analyses.}
    \centering
    \begin{tabular}{ l l l l l }
        \toprule
        & \multicolumn{4}{c}{Priors} \\
        \cmidrule(){2-5}
        Model & \divTimeIndexVector & \divTime{} & \ancestralTheta{} & \descendantTheta{}{} \\
        \midrule
            \modelOld & $\divTimeIndexVector \sim \priorOld$
                      & $\divTime{} \sim U(0,10)$
                      & $\ancestralTheta{} \sim U(0, 0.05)$
                      & $\descendantThetaMean{} \sim U(0, 0.05)$ \\
            \modelDPP & $\divTimeIndexVector \sim \priorDPP{\sim Gamma(\cdot,\cdot)}$
                      & $\divTime{} \sim Exp(0.3464)$
                      & $\ancestralTheta{} \sim Exp(40)$
                      & $\descendantTheta{}{} \sim Exp(40)$ \\
            \modelUniform & $\divTimeIndexVector \sim \priorUniform$
                          & $\divTime{} \sim Exp(0.3464)$
                          & $\ancestralTheta{} \sim Exp(40)$
                          & $\descendantTheta{}{} \sim Exp(40)$ \\
            \modelUshaped & $\divTimeIndexVector \sim \priorOld$
                          & $\divTime{} \sim Exp(0.3464)$
                          & $\ancestralTheta{} \sim Exp(40)$
                          & $\descendantTheta{}{} \sim Exp(40)$ \\
        \bottomrule
    \end{tabular}
    \label{tabPriors}
\end{table}

@@

@@

@@

        assessing the power of the models in Table \ref{tabPriors}.
        latter assuming a per-site rate of 1\e{-8} mutations per generation.}

@@

    \begin{tabular}{ l l l l l l }

@@

        & \multicolumn{5}{c}{Priors} \\
        \cmidrule(){2-6}
        Model series & \divTimeIndexVector & \divTime{} (\globalcoalunit gens.) & \divTime{} (MGA) & \ancestralTheta{} & \descendantTheta{}{} \\

@@

                            & $\divTime{} \sim U(0,0.2)$
                            & $\divTime{} \sim U(0,0.5)$

@@

                            & $\divTime{} \sim U(0,0.4)$
                            & $\divTime{} \sim U(0,1.0)$

@@

                            & $\divTime{} \sim U(0,0.6)$
                            & $\divTime{} \sim U(0,1.5)$

@@

                            & $\divTime{} \sim U(0,0.8)$
                            & $\divTime{} \sim U(0,2.0)$

@@

                            & $\divTime{} \sim U(0,1.0)$
                            & $\divTime{} \sim U(0,2.5)$

@@

                            & $\divTime{} \sim U(0,2.0)$
                            & $\divTime{} \sim U(0,5.0)$

@@

                            & $\divTime{} \sim U(0,0.2)$
                            & $\divTime{} \sim U(0,0.5)$
                            & $\ancestralTheta{} \sim Exp(40)$
                            & $\descendantTheta{}{} \sim Exp(40)$ \\

@@

                            & $\divTime{} \sim U(0,0.4)$
                            & $\divTime{} \sim U(0,1.0)$
                            & $\ancestralTheta{} \sim Exp(40)$
                            & $\descendantTheta{}{} \sim Exp(40)$ \\

@@

                            & $\divTime{} \sim U(0,0.6)$
                            & $\divTime{} \sim U(0,1.5)$
                            & $\ancestralTheta{} \sim Exp(40)$
                            & $\descendantTheta{}{} \sim Exp(40)$ \\

@@

                            & $\divTime{} \sim U(0,0.8)$
                            & $\divTime{} \sim U(0,2.0)$
                            & $\ancestralTheta{} \sim Exp(40)$
                            & $\descendantTheta{}{} \sim Exp(40)$ \\

@@

                            & $\divTime{} \sim U(0,1.0)$
                            & $\divTime{} \sim U(0,2.5)$
                            & $\ancestralTheta{} \sim Exp(40)$
                            & $\descendantTheta{}{} \sim Exp(40)$ \\

@@

                            & $\divTime{} \sim U(0,2.0)$
                            & $\divTime{} \sim U(0,5.0)$
                            & $\ancestralTheta{} \sim Exp(40)$
                            & $\descendantTheta{}{} \sim Exp(40)$ \\

@@

                            & $\divTime{} \sim Exp(17.32)$
                            & $\divTime{} \sim Exp(mean = 0.14)$
                            & $\ancestralTheta{} \sim Exp(40)$
                            & $\descendantTheta{}{} \sim Exp(40)$ \\

@@

                            & $\divTime{} \sim Exp(8.66)$
                            & $\divTime{} \sim Exp(mean = 0.29)$
                            & $\ancestralTheta{} \sim Exp(40)$
                            & $\descendantTheta{}{} \sim Exp(40)$ \\

@@

                            & $\divTime{} \sim Exp(5.77)$
                            & $\divTime{} \sim Exp(mean = 0.43)$
                            & $\ancestralTheta{} \sim Exp(40)$
                            & $\descendantTheta{}{} \sim Exp(40)$ \\

@@

                            & $\divTime{} \sim Exp(4.33)$
                            & $\divTime{} \sim Exp(mean = 0.58)$
                            & $\ancestralTheta{} \sim Exp(40)$
                            & $\descendantTheta{}{} \sim Exp(40)$ \\

@@

                            & $\divTime{} \sim Exp(3.46)$
                            & $\divTime{} \sim Exp(mean = 0.72)$
                            & $\ancestralTheta{} \sim Exp(40)$
                            & $\descendantTheta{}{} \sim Exp(40)$ \\

@@

                            & $\divTime{} \sim Exp(1.73)$
                            & $\divTime{} \sim Exp(mean = 1.44)$
                            & $\ancestralTheta{} \sim Exp(40)$
                            & $\descendantTheta{}{} \sim Exp(40)$ \\

@@

                      $\divTime{} \sim U(0,34.64)$ \tb
                      $\divTime{} \sim U(0,17.3 \; MGA)$ \tb

@@

                      $\divTime{} \sim Exp(0.1)$ \tb
                      $\divTime{} \sim Exp(mean=5 \; MGA)$ \tb
                      $\ancestralTheta{} \sim Exp(200)$ \tb
                      $\descendantTheta{1}{} \sim Exp(200)$ \tb
                      $\descendantTheta{2}{} \sim Exp(200)$ \tb

@@

                      $\divTime{} \sim Exp(1/6)$ \tb
                      $\divTime{} \sim Exp(mean=3 \; MGA)$ \tb
                      $\ancestralTheta{} \sim Exp(200)$ \tb
                      $\descendantTheta{1}{} \sim Exp(200)$ \tb
                      $\descendantTheta{2}{} \sim Exp(200)$ \tb

@@

                      $\divTime{} \sim Exp(0.1)$ \tb
                      $\divTime{} \sim Exp(mean=5 \; MGA)$ \tb
                      $\ancestralTheta{} = \descendantTheta{1}{} = \descendantTheta{2}{} \sim Exp(200)$ \tb

@@

                      $\divTime{} \sim Exp(0.1)$ \tb
                      $\divTime{} \sim Exp(mean=5 \; MGA)$ \tb
                      $\ancestralTheta{} \sim Exp(200)$ \tb
                      $\descendantTheta{1}{} = \descendantTheta{2}{} \sim Exp(200)$ \tb

>>>>

\begin{table}[htbp]
    \sffamily
    \footnotesize
    \addtolength{\tabcolsep}{-0.08cm}
    \rowcolors{2}{}{myGray}
    %\captionsetup{font=footnotesize}
    \caption{The model priors evaluated in our simulation-based analyses.  For
        the \modelDPP model, the prior on the concentration parameter,
        $\concentrationParam \sim Gamma(\cdot,\cdot)$, was set to $Gamma(2,2)$
        for the validation analyses and $Gamma(1.5,18.1)$ for the power
        analyses. The distributions of divergence times are given in units of
        \globalcoalunit generations followed in brackets by units of millions
        of generations ago (MGA), with the former converted to the latter
        assuming a per-site rate of 1\e{-8} mutations per generation. For model
        \modelOld, the priors for theta parameters are $\ancestralTheta{} \sim
        U(0, 0.05)$ and $\descendantTheta{1}{}, \descendantTheta{2}{} \sim
        Beta(1, 1) \times 2 \times U(0, 0.05)$. The later is summarized as
        $\descendantThetaMean{} \sim U(0, 0.05)$. For the \modelDPP and
        \modelUniform, and \modelUshaped models, \ancestralTheta{},
        \descendantTheta{1}{}, and \descendantTheta{2}{} are independently
        and exponentially distributed with a mean of 0.025.}
    \centering
    \begin{tabular}{ l l l l l }
        \toprule
        & \multicolumn{4}{c}{Priors} \\
        \cmidrule(){2-5}
        Model & \divTimeIndexVector & \divTime{} & \myTheta{} &  \\
        \midrule
            \modelOld & $\divTimeIndexVector \sim \priorOld$
                      & $\divTime{} \sim U(0,10 \; [25 \; MGA])$
                      & $\ancestralTheta{} \sim U(0, 0.05)$
                      & $\descendantThetaMean{} \sim U(0, 0.05)$ \\
            \modelDPP & $\divTimeIndexVector \sim \priorDPP{\sim Gamma(\cdot,\cdot)}$
                      & $\divTime{} \sim Exp(mean=2.887 \; [7.22 \; MGA])$
                      & \multicolumn{2}{l}{$\ancestralTheta{} \sim \descendantTheta{1}{} \sim \descendantTheta{2}{} \sim Exp(mean=0.025)$} \\
            \modelUniform & $\divTimeIndexVector \sim \priorUniform$
                          & $\divTime{} \sim Exp(mean=2.887 \; [7.22 \; MGA])$
                          & \multicolumn{2}{l}{$\ancestralTheta{} \sim \descendantTheta{1}{} \sim \descendantTheta{2}{} \sim Exp(mean=0.025)$} \\
            \modelUshaped & $\divTimeIndexVector \sim \priorOld$
                          & $\divTime{} \sim Exp(mean=2.887 \; [7.22 \; MGA])$
                          & \multicolumn{2}{l}{$\ancestralTheta{} \sim \descendantTheta{1}{} \sim \descendantTheta{2}{} \sim Exp(mean=0.025)$} \\
        \bottomrule
    \end{tabular}
    \label{tabPriors}
\end{table}

@@

    % \scriptsize

@@

    % \captionsetup{font=footnotesize}

@@

        assessing the power of the models in Table \ref{tabPriors}.  The
        distributions of divergence times are given in units of \globalcoalunit
        generations followed in brackets by units of millions of generations
        ago (MGA), with the former converted to the latter assuming a per-site
        rate of 1\e{-8} mutations per generation. For all of the
        \powerSeriesOld models, the priors for theta parameters are
        $\ancestralTheta{} \sim U(0, 0.05)$ and $\descendantTheta{1}{},
        \descendantTheta{2}{} \sim Beta(1, 1) \times 2 \times U(0, 0.05)$. The
        later is summarized as $\descendantThetaMean{} \sim U(0, 0.05)$. For
        the \powerSeriesUniform and \powerSeriesExp models, \ancestralTheta{},
        \descendantTheta{1}{}, and \descendantTheta{2}{} are independently
        and exponentially distributed with a mean of 0.025.}

@@

    \begin{tabular}{ l l l l l }

@@

        & \multicolumn{4}{c}{Priors} \\
        \cmidrule(){2-5}
        Model series & \divTimeIndexVector & \divTime{} & \myTheta{} &  \\

@@

                            & $\divTime{} \sim U(0,0.2 \; [0.5 \; MGA])$

@@

                            & $\divTime{} \sim U(0,0.4 \; [1.0 \; MGA])$

@@

                            & $\divTime{} \sim U(0,0.6 \; [1.5 \; MGA])$

@@

                            & $\divTime{} \sim U(0,0.8 \; [2.0 \; MGA])$

@@

                            & $\divTime{} \sim U(0,1.0 \; [2.5 \; MGA])$

@@

                            & $\divTime{} \sim U(0,2.0 \; [5.0 \; MGA])$

@@

                            & $\divTime{} \sim U(0,0.2 \; [0.5 \; MGA])$
                            & \multicolumn{2}{l}{$\ancestralTheta{} \sim \descendantTheta{1}{} \sim \descendantTheta{2}{} \sim Exp(mean=0.025)$} \\

@@

                            & $\divTime{} \sim U(0,0.4 \; [1.0 \; MGA])$
                            & \multicolumn{2}{l}{$\ancestralTheta{} \sim \descendantTheta{1}{} \sim \descendantTheta{2}{} \sim Exp(mean=0.025)$} \\

@@

                            & $\divTime{} \sim U(0,0.6 \; [1.5 \; MGA])$
                            & \multicolumn{2}{l}{$\ancestralTheta{} \sim \descendantTheta{1}{} \sim \descendantTheta{2}{} \sim Exp(mean=0.025)$} \\

@@

                            & $\divTime{} \sim U(0,0.8 \; [2.0 \; MGA])$
                            & \multicolumn{2}{l}{$\ancestralTheta{} \sim \descendantTheta{1}{} \sim \descendantTheta{2}{} \sim Exp(mean=0.025)$} \\

@@

                            & $\divTime{} \sim U(0,1.0 \; [2.5 \; MGA])$
                            & \multicolumn{2}{l}{$\ancestralTheta{} \sim \descendantTheta{1}{} \sim \descendantTheta{2}{} \sim Exp(mean=0.025)$} \\

@@

                            & $\divTime{} \sim U(0,2.0 \; [5.0 \; MGA])$
                            & \multicolumn{2}{l}{$\ancestralTheta{} \sim \descendantTheta{1}{} \sim \descendantTheta{2}{} \sim Exp(mean=0.025)$} \\

@@

                            & $\divTime{} \sim Exp(mean = 0.058 \; [0.14 \; MGA])$
                            & \multicolumn{2}{l}{$\ancestralTheta{} \sim \descendantTheta{1}{} \sim \descendantTheta{2}{} \sim Exp(mean=0.025)$} \\

@@

                            & $\divTime{} \sim Exp(mean = 0.115 \; [0.29 \; MGA])$
                            & \multicolumn{2}{l}{$\ancestralTheta{} \sim \descendantTheta{1}{} \sim \descendantTheta{2}{} \sim Exp(mean=0.025)$} \\

@@

                            & $\divTime{} \sim Exp(mean = 0.173 \; [0.43 \; MGA])$
                            & \multicolumn{2}{l}{$\ancestralTheta{} \sim \descendantTheta{1}{} \sim \descendantTheta{2}{} \sim Exp(mean=0.025)$} \\

@@

                            & $\divTime{} \sim Exp(mean = 0.231 \; [0.58 \; MGA])$
                            & \multicolumn{2}{l}{$\ancestralTheta{} \sim \descendantTheta{1}{} \sim \descendantTheta{2}{} \sim Exp(mean=0.025)$} \\

@@

                            & $\divTime{} \sim Exp(mean = 0.289 \; [0.72 \; MGA])$
                            & \multicolumn{2}{l}{$\ancestralTheta{} \sim \descendantTheta{1}{} \sim \descendantTheta{2}{} \sim Exp(mean=0.025)$} \\

@@

                            & $\divTime{} \sim Exp(mean = 0.577 \; [1.44 \; MGA])$
                            & \multicolumn{2}{l}{$\ancestralTheta{} \sim \descendantTheta{1}{} \sim \descendantTheta{2}{} \sim Exp(mean=0.025)$} \\

@@

        $\divTime{} \sim U(0,34.64 \, [17.3 \; MGA])$ \tb

@@

                      $\divTime{} \sim Exp(mean=10 \; [5 \; MGA])$ \tb
                      $\ancestralTheta{} \sim Exp(mean=0.005)$ \tb
                      $\descendantTheta{1}{} \sim Exp(mean=0.005)$ \tb
                      $\descendantTheta{2}{} \sim Exp(mean=0.005)$ \tb

@@

                      $\divTime{} \sim Exp(mean=6 \; [3 \; MGA])$ \tb
                      $\ancestralTheta{} \sim Exp(mean=0.005)$ \tb
                      $\descendantTheta{1}{} \sim Exp(mean=0.005)$ \tb
                      $\descendantTheta{2}{} \sim Exp(mean=0.005)$ \tb

@@

                      $\divTime{} \sim Exp(mean=10 \; [5 \; MGA])$ \tb
                      $\ancestralTheta{} = \descendantTheta{1}{} = \descendantTheta{2}{} \sim Exp(mean=0.005)$ \tb

@@

                      $\divTime{} \sim Exp(mean=10 \; [5 \; MGA])$ \tb
                      $\ancestralTheta{} \sim Exp(mean=0.005)$ \tb
                      $\descendantTheta{1}{} = \descendantTheta{2}{} \sim Exp(mean=0.005)$ \tb
